---
title: "ClassificationTree"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r message=FALSE, warning=FALSE, include=FALSE}
# echo=FALSE will stop the code chunk from appearing in the knit document
# warning=FALSE and message=FALSE will stop R messages from appearing in the knit document
library(tidyverse)

library(rpart)
library(partykit)
protein <- read_csv("STA130_Course_Project.csv")
course_project <- protein
course_project_ori <- protein
```

## Results of the Classification tree at time 0.5h
```{r include=FALSE}
course_project_2 <- course_project_ori %>% filter(Timepoint == '0.5 h', 
                                                  drug_id == 1, dose_id == 2, 
                                                  Rep == 1)

tree <- rpart(NGFR ~ ATF2+ATF3+ATF4+ATF5+Phospho_ATF1+
                Phospho_ATF2+
                Phospho_ATF4+ATF6+JunB+	c_Jun+JunD+Phospho_S6+Phospho_c_Jun+
                Phospho_Erk1+NF_kappaB+Fra1+Fra2+
                c_Fos+Ki_67+Phospho_Fra1+Phospho_c_Fos+Phospho_p38, 
              data=course_project_2)
tree %>% as.party() %>% plot(type="simple",
tp_args = list(FUN = function(info) list(format(info$prediction), format(paste("n =",info$n)),
format(paste(round(info$err,0.0001),"% err",sep="")))))
plot(as.party(tree), gp=gpar(cex=1), type="simple")
```
```{r echo=FALSE}
barplot(t(tree$variable.importance),horiz=TRUE)
```

## Results of the Classification tree at time 2h
```{r include=FALSE}
course_project_2 <- course_project_ori %>% filter(Timepoint == '2 h', 
                                                  drug_id == 1, dose_id == 2, 
                                                  Rep == 1)

tree <- rpart(NGFR ~ ATF2+ATF3+ATF4+ATF5+Phospho_ATF1+
                Phospho_ATF2+
                Phospho_ATF4+ATF6+JunB+	c_Jun+JunD+Phospho_S6+Phospho_c_Jun+
                Phospho_Erk1+NF_kappaB+Fra1+Fra2+
                c_Fos+Ki_67+Phospho_Fra1+Phospho_c_Fos+Phospho_p38, 
              data=course_project_2)
tree %>% as.party() %>% plot(type="simple",
tp_args = list(FUN = function(info) list(format(info$prediction), format(paste("n =",info$n)),
format(paste(round(info$err,0.0001),"% err",sep="")))))
plot(as.party(tree), gp=gpar(cex=1), type="simple")
```
```{r echo=FALSE}
barplot(t(tree$variable.importance),horiz=TRUE)
```

## Results of Classification tree at time 6h
```{r include=FALSE}
course_project_2 <- course_project_ori %>% filter(Timepoint == '6 h', 
                                                  drug_id == 1, dose_id == 2, 
                                                  Rep == 1)

tree <- rpart(NGFR ~ ATF2+ATF3+ATF4+ATF5+Phospho_ATF1+
                Phospho_ATF2+
                Phospho_ATF4+ATF6+JunB+	c_Jun+JunD+Phospho_S6+Phospho_c_Jun+
                Phospho_Erk1+NF_kappaB+Fra1+Fra2+
                c_Fos+Ki_67+Phospho_Fra1+Phospho_c_Fos+Phospho_p38, 
              data=course_project_2)
tree %>% as.party() %>% plot(type="simple",
tp_args = list(FUN = function(info) list(format(info$prediction), format(paste("n =",info$n)),
format(paste(round(info$err,0.0001),"% err",sep="")))))
plot(as.party(tree), gp=gpar(cex=1), type="simple")
```
```{r echo=FALSE}
barplot(t(tree$variable.importance),horiz=TRUE)
```

## Results of the Classification tree at time 15h
```{r include=FALSE}
course_project_2 <- course_project_ori %>% filter(Timepoint == '15 h', 
                                                  drug_id == 1, dose_id == 2, 
                                                  Rep == 1)

tree <- rpart(NGFR ~ ATF2+ATF3+ATF4+ATF5+Phospho_ATF1+
                Phospho_ATF2+
                Phospho_ATF4+ATF6+JunB+	c_Jun+JunD+Phospho_S6+Phospho_c_Jun+
                Phospho_Erk1+NF_kappaB+Fra1+Fra2+
                c_Fos+Ki_67+Phospho_Fra1+Phospho_c_Fos+Phospho_p38, 
              data=course_project_2)
tree %>% as.party() %>% plot(type="simple",
tp_args = list(FUN = function(info) list(format(info$prediction), format(paste("n =",info$n)),
format(paste(round(info$err,0.0001),"% err",sep="")))))
plot(as.party(tree), gp=gpar(cex=1), type="simple")
```
```{r echo=FALSE}
barplot(t(tree$variable.importance),horiz=TRUE)
```

## Results of the Classification tree at time 24h
```{r include=FALSE}
course_project_2 <- course_project_ori %>% filter(Timepoint == '24 h', 
                                                  drug_id == 1, dose_id == 2, 
                                                  Rep == 1)

tree <- rpart(NGFR ~ ATF2+ATF3+ATF4+ATF5+Phospho_ATF1+
                Phospho_ATF2+
                Phospho_ATF4+ATF6+JunB+	c_Jun+JunD+Phospho_S6+Phospho_c_Jun+
                Phospho_Erk1+NF_kappaB+Fra1+Fra2+
                c_Fos+Ki_67+Phospho_Fra1+Phospho_c_Fos+Phospho_p38, 
              data=course_project_2)
tree %>% as.party() %>% plot(type="simple",
tp_args = list(FUN = function(info) list(format(info$prediction), format(paste("n =",info$n)),
format(paste(round(info$err,0.0001),"% err",sep="")))))
plot(as.party(tree), gp=gpar(cex=1), type="simple")
```
```{r echo=FALSE}
barplot(t(tree$variable.importance),horiz=TRUE)
```

## Results of the Classification tree at time 72h
```{r include=FALSE}
course_project_2 <- course_project_ori %>% filter(Timepoint == '72 h', 
                                                  drug_id == 1, dose_id == 2, 
                                                  Rep == 1)

tree <- rpart(NGFR ~ ATF2+ATF3+ATF4+ATF5+Phospho_ATF1+
                Phospho_ATF2+
                Phospho_ATF4+ATF6+JunB+	c_Jun+JunD+Phospho_S6+Phospho_c_Jun+
                Phospho_Erk1+NF_kappaB+Fra1+Fra2+
                c_Fos+Ki_67+Phospho_Fra1+Phospho_c_Fos+Phospho_p38, 
              data=course_project_2)
tree %>% as.party() %>% plot(type="simple",
tp_args = list(FUN = function(info) list(format(info$prediction), format(paste("n =",info$n)),
format(paste(round(info$err,0.0001),"% err",sep="")))))
plot(as.party(tree), gp=gpar(cex=1), type="simple")
```
```{r echo=FALSE}
barplot(t(tree$variable.importance),horiz=TRUE)
```


## Results of the Classification tree at time '120 h'
```{r include=FALSE}
course_project_2 <- course_project_ori %>% filter(Timepoint == '120 h', 
                                                  drug_id == 1, dose_id == 2, 
                                                  Rep == 1)

tree <- rpart(NGFR ~ ATF2+ATF3+ATF4+ATF5+Phospho_ATF1+
                Phospho_ATF2+
                Phospho_ATF4+ATF6+JunB+	c_Jun+JunD+Phospho_S6+Phospho_c_Jun+
                Phospho_Erk1+NF_kappaB+Fra1+Fra2+
                c_Fos+Ki_67+Phospho_Fra1+Phospho_c_Fos+Phospho_p38, 
              data=course_project_2)
tree %>% as.party() %>% plot(type="simple",
tp_args = list(FUN = function(info) list(format(info$prediction), format(paste("n =",info$n)),
format(paste(round(info$err,0.0001),"% err",sep="")))))
plot(as.party(tree), gp=gpar(cex=1), type="simple")
```
```{r echo=FALSE}
barplot(t(tree$variable.importance),horiz=TRUE)
```

## Results of the Classification tree at time 0.5h
```{r include=FALSE}
course_project_2 <- course_project_ori %>% filter(Timepoint == '0.5 h', 
                                                  drug_id == 1, dose_id == 2, 
                                                  Rep == 1)

tree <- rpart(Sox10 ~ ATF2+ATF3+ATF4+ATF5+Phospho_ATF1+
                Phospho_ATF2+
                Phospho_ATF4+ATF6+JunB+	c_Jun+JunD+Phospho_S6+Phospho_c_Jun+
                Phospho_Erk1+NF_kappaB+Fra1+Fra2+
                c_Fos+Ki_67+Phospho_Fra1+Phospho_c_Fos+Phospho_p38, 
              data=course_project_2)
tree %>% as.party() %>% plot(type="simple",
tp_args = list(FUN = function(info) list(format(info$prediction), format(paste("n =",info$n)),
format(paste(round(info$err,0.0001),"% err",sep="")))))
plot(as.party(tree), gp=gpar(cex=1), type="simple")
```
```{r echo=FALSE}
barplot(t(tree$variable.importance),horiz=TRUE)
```

## Results of the Classification tree at time 2h
```{r include=FALSE}
course_project_2 <- course_project_ori %>% filter(Timepoint == '2 h', 
                                                  drug_id == 1, dose_id == 2, 
                                                  Rep == 1)

tree <- rpart(Sox10 ~ ATF2+ATF3+ATF4+ATF5+Phospho_ATF1+
                Phospho_ATF2+
                Phospho_ATF4+ATF6+JunB+	c_Jun+JunD+Phospho_S6+Phospho_c_Jun+
                Phospho_Erk1+NF_kappaB+Fra1+Fra2+
                c_Fos+Ki_67+Phospho_Fra1+Phospho_c_Fos+Phospho_p38, 
              data=course_project_2)
tree %>% as.party() %>% plot(type="simple",
tp_args = list(FUN = function(info) list(format(info$prediction), format(paste("n =",info$n)),
format(paste(round(info$err,0.0001),"% err",sep="")))))
plot(as.party(tree), gp=gpar(cex=1), type="simple")
```
```{r echo=FALSE}
barplot(t(tree$variable.importance),horiz=TRUE)
```

## Results of Classification tree at time 6h
```{r include=FALSE}
course_project_2 <- course_project_ori %>% filter(Timepoint == '6 h', 
                                                  drug_id == 1, dose_id == 2, 
                                                  Rep == 1)

tree <- rpart(Sox10 ~ ATF2+ATF3+ATF4+ATF5+Phospho_ATF1+
                Phospho_ATF2+
                Phospho_ATF4+ATF6+JunB+	c_Jun+JunD+Phospho_S6+Phospho_c_Jun+
                Phospho_Erk1+NF_kappaB+Fra1+Fra2+
                c_Fos+Ki_67+Phospho_Fra1+Phospho_c_Fos+Phospho_p38, 
              data=course_project_2)
tree %>% as.party() %>% plot(type="simple",
tp_args = list(FUN = function(info) list(format(info$prediction), format(paste("n =",info$n)),
format(paste(round(info$err,0.0001),"% err",sep="")))))
plot(as.party(tree), gp=gpar(cex=1), type="simple")
```
```{r echo=FALSE}
barplot(t(tree$variable.importance),horiz=TRUE)
```

## Results of the Classification tree at time 15h
```{r include=FALSE}
course_project_2 <- course_project_ori %>% filter(Timepoint == '15 h', 
                                                  drug_id == 1, dose_id == 2, 
                                                  Rep == 1)

tree <- rpart(Sox10 ~ ATF2+ATF3+ATF4+ATF5+Phospho_ATF1+
                Phospho_ATF2+
                Phospho_ATF4+ATF6+JunB+	c_Jun+JunD+Phospho_S6+Phospho_c_Jun+
                Phospho_Erk1+NF_kappaB+Fra1+Fra2+
                c_Fos+Ki_67+Phospho_Fra1+Phospho_c_Fos+Phospho_p38, 
              data=course_project_2)
tree %>% as.party() %>% plot(type="simple",
tp_args = list(FUN = function(info) list(format(info$prediction), format(paste("n =",info$n)),
format(paste(round(info$err,0.0001),"% err",sep="")))))
plot(as.party(tree), gp=gpar(cex=1), type="simple")
```
```{r echo=FALSE}
barplot(t(tree$variable.importance),horiz=TRUE)
```

## Results of the Classification tree at time 24h
```{r include=FALSE}
course_project_2 <- course_project_ori %>% filter(Timepoint == '24 h', 
                                                  drug_id == 1, dose_id == 2, 
                                                  Rep == 1)

tree <- rpart(Sox10 ~ ATF2+ATF3+ATF4+ATF5+Phospho_ATF1+
                Phospho_ATF2+
                Phospho_ATF4+ATF6+JunB+	c_Jun+JunD+Phospho_S6+Phospho_c_Jun+
                Phospho_Erk1+NF_kappaB+Fra1+Fra2+
                c_Fos+Ki_67+Phospho_Fra1+Phospho_c_Fos+Phospho_p38, 
              data=course_project_2)
tree %>% as.party() %>% plot(type="simple",
tp_args = list(FUN = function(info) list(format(info$prediction), format(paste("n =",info$n)),
format(paste(round(info$err,0.0001),"% err",sep="")))))
plot(as.party(tree), gp=gpar(cex=1), type="simple")
```
```{r echo=FALSE}
barplot(t(tree$variable.importance),horiz=TRUE)
```

## Results of the Classification tree at time 72h
```{r include=FALSE}
course_project_2 <- course_project_ori %>% filter(Timepoint == '72 h', 
                                                  drug_id == 1, dose_id == 2, 
                                                  Rep == 1)

tree <- rpart(Sox10 ~ ATF2+ATF3+ATF4+ATF5+Phospho_ATF1+
                Phospho_ATF2+
                Phospho_ATF4+ATF6+JunB+	c_Jun+JunD+Phospho_S6+Phospho_c_Jun+
                Phospho_Erk1+NF_kappaB+Fra1+Fra2+
                c_Fos+Ki_67+Phospho_Fra1+Phospho_c_Fos+Phospho_p38, 
              data=course_project_2)
tree %>% as.party() %>% plot(type="simple",
tp_args = list(FUN = function(info) list(format(info$prediction), format(paste("n =",info$n)),
format(paste(round(info$err,0.0001),"% err",sep="")))))
plot(as.party(tree), gp=gpar(cex=1), type="simple")
```
```{r echo=FALSE}
barplot(t(tree$variable.importance),horiz=TRUE)
```


## Results of the Classification tree at time '120 h'
```{r include=FALSE}
course_project_2 <- course_project_ori %>% filter(Timepoint == '120 h', 
                                                  drug_id == 1, dose_id == 2, 
                                                  Rep == 1)

tree <- rpart(Sox10 ~ ATF2+ATF3+ATF4+ATF5+Phospho_ATF1+
                Phospho_ATF2+
                Phospho_ATF4+ATF6+JunB+	c_Jun+JunD+Phospho_S6+Phospho_c_Jun+
                Phospho_Erk1+NF_kappaB+Fra1+Fra2+
                c_Fos+Ki_67+Phospho_Fra1+Phospho_c_Fos+Phospho_p38, 
              data=course_project_2)
tree %>% as.party() %>% plot(type="simple",
tp_args = list(FUN = function(info) list(format(info$prediction), format(paste("n =",info$n)),
format(paste(round(info$err,0.0001),"% err",sep="")))))
plot(as.party(tree), gp=gpar(cex=1), type="simple")
```
```{r echo=FALSE}
barplot(t(tree$variable.importance),horiz=TRUE)
```

